\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{parskip}

\geometry{margin=2.5cm}

% Code style
\definecolor{codebg}{RGB}{245,245,245}
\definecolor{keyword}{RGB}{0,112,0}
\definecolor{comment}{RGB}{128,128,128}
\definecolor{string}{RGB}{180,0,0}

\lstdefinestyle{pythonstyle}{
    backgroundcolor=\color{codebg},
    basicstyle=\ttfamily\small,
    keywordstyle=\color{keyword}\bfseries,
    stringstyle=\color{string},
    commentstyle=\color{comment}\itshape,
    language=Python,
    frame=single,
    rulecolor=\color{gray!40},
    breaklines=true,
    showstringspaces=false,
    tabsize=4,
    captionpos=b,
}

\title{\textbf{Wind Turbine Blade Fault Classification\\Using a Simple CNN}\\[0.5em]
\large Step 1 --- Import Libraries}
\author{Amreen Batool}
\date{}

\begin{document}
\maketitle

\section*{Step 1 --- Import Libraries}

\begin{lstlisting}[style=pythonstyle]
import os
os.environ["CUDA_VISIBLE_DEVICES"] = "-1"  # Use CPU and avoid GPU/CUDA issues

import tensorflow as tf
from tensorflow.keras.preprocessing.image import ImageDataGenerator
from tensorflow.keras import layers, models
from tensorflow.keras.callbacks import EarlyStopping
import matplotlib.pyplot as plt
import numpy as np
from sklearn.metrics import confusion_matrix, classification_report
import seaborn as sns
\end{lstlisting}

\subsection*{Explanation}

\begin{itemize}
    \item \texttt{os} is used for folder operations.
    \item \texttt{os.environ["CUDA\_VISIBLE\_DEVICES"] = "-1"} disables GPU and forces CPU use.
    \item \texttt{tensorflow} is the deep learning library.
    \item \texttt{ImageDataGenerator} loads and preprocesses images.
    \item \texttt{layers, models} are used to build the CNN.
    \item \texttt{EarlyStopping} stops training when validation performance stops improving.
    \item \texttt{matplotlib} is used for plots.
    \item \texttt{numpy} is used for arrays and predictions.
    \item \texttt{confusion\_matrix} and \texttt{classification\_report} evaluate classification performance.
    \item \texttt{seaborn} makes the confusion matrix look better.
\end{itemize}

\end{document}
